# library
```{r}
library(tidyverse)
library(factoextra)
library(cluster)
library(FactoMineR)
library(factoextra)
library(corrplot)
library(dplyr)
library(ggplot2)
library(clustMixType)
library(magrittr)
library(ISLR)
library(Rtsne)
library(RColorBrewer)
```

# Data Cleaning
```{r}
data<-read.csv("CFM_Campaigns.csv")
unique(data$sales_country)
data1<-data[data$sales_country=="USA",]
data1<-data1[,-3]
data1<-data1[,-2]
class(data1$houseowner)
data1$houseowner<-ifelse(data1$houseowner=="Y",TRUE,FALSE)
data1<-data1[,-6]
data1$gender<-ifelse(data1$gender=="F",0,1)
```

```{r}
unique(data1$store_type)
data1$store_type_1<-ifelse(data1$store_type=="Deluxe Supermarket",4,data1$store_type)
data1$store_type_1<-ifelse(data1$store_type_1=="Supermarket",3,data1$store_type_1)
data1$store_type_1<-ifelse(data1$store_type_1=="Gourmet Supermarket",2,data1$store_type_1)
data1$store_type_1<-ifelse(data1$store_type_1=="Small Grocery",1,data1$store_type_1)
```

```{r}
data1$marital_status<-ifelse(data1$marital_status=="M",TRUE,FALSE)
```

```{r}
unique(data1$media_type)
data1$radio<-str_detect(data1$media_type,"Radio")
data1$Daily_Paper<-str_detect(data1$media_type,"Daily Paper")
data1$In_Store_Coupon<-str_detect(data1$media_type,"In-Store Coupon")
data1$Product_Attachment<-str_detect(data1$media_type,"Product Attachment")
data1$Sunday_Paper<-str_detect(data1$media_type,"Sunday Paper")
data1$Street_Handout<-str_detect(data1$media_type,"Street Handout")
data1$Cash_Register_Handout<-str_detect(data1$media_type,"Cash Register Handout")
data1$Bulk_Mail<-str_detect(data1$media_type,"Bulk Mail" )
store_data<-data1
```

# PCA

This part aims to determine whether there is a relationship between campaign cost and the store's attributes. Due to the many correlated variables, PCA transforms them into a much smaller set of uncorrelated variables called *principal components*. The store attributes and promotion data include:
1.*Numeric data*: "store_sales.in.millions.","store_cost.in.millions.", "unit_sales.in.millions.", "SRP"(Suggested retail price), "gross_weight", "net_weight", "store_sqft", "grocery_sqft","frozen_sqft", "meat_sqft";
2.*Categorical data*: "coffee_bar", "video_store", "salad_bar", "prepared_food", "florist",radio", "Daily_Paper", "In_Store_Coupon", "Product_Attachment", "Sunday_Paper", "Street_Handout", "Cash_Register_Handout", "Bulk_Mail";
For numeric data, PCA technique can be applied without any data cleaning. But for categorical data, the challenge is to find a suitable way to represent distances between variable categories and individuals in the factorial space. Therefore, all categorical data are summarized to show the number of different displays and services of stores. All the store attributes are converted to numeric data now.
Additionally, different stores might have different effects of campaign cost; Deluxe Supermarket, Supermarket, Gourmet Supermarket, and Small Grocery, are sorted to do the PCA analysis:
Deluxe Supermarket=4, Supermarket=3,Gourmet Supermarket=2, Small Grocery=1.


```{r}
store_data_sample<-store_data[sample(nrow(store_data),8000),]
```

```{r}
store_data_sample$media<-store_data_sample[,39]+store_data_sample[,40]+store_data_sample[,41]+store_data_sample[,42]+store_data_sample[,43]+store_data_sample[,44]+store_data_sample[,45]+store_data_sample[,46]
store_data_sample_pca<-store_data_sample[,-c(39:46)]
```

```{r}
store_data_sample_pca$extra<-store_data_sample_pca[31]+store_data_sample_pca[32]+store_data_sample_pca[33]+store_data_sample_pca[34]+store_data_sample_pca[35]
store_data_sample_pca<-store_data_sample_pca[,-c(1,5:17,24:26,31:36)]
```

```{r}
store_data_sample_pca_1<-store_data_sample_pca[store_data_sample_pca$store_type_1==1,]
store_data_sample_pca_2<-store_data_sample_pca[store_data_sample_pca$store_type_1==2,]
store_data_sample_pca_3<-store_data_sample_pca[store_data_sample_pca$store_type_1==3,]
store_data_sample_pca_4<-store_data_sample_pca[store_data_sample_pca$store_type_1==4,]
```

## Small grocery
The scree plot shows that 4 PCs are the best for small grocery. For visualisation purposes, we use the first four components. 

PC 1 explains about 34% of the variability, PC 2 explains about 24%, PC 3 explains about 16%, and PC 4 explains about 8% of the variability. The second and third graph both shows the correlation among variables. Arrows are closer to each other, indicating a high correlation. 
*PC 1* is positively and highly correlated with the variables store_sqft, grocery_sqft, frozen_sqft, meat_sqft. *PC 2* is positively correlated with "store_sales.in.millions.","store_cost.in.millions.", "unit_sales.in.millions.". *PC 3* is positively and highly correlated with "gross_weight" and "net_weight". *PC 4* is positively and highly correlated with "units_per_case" and "media". Therefore, based on the correlation, Dim 1 is interpreted as "features", dim 2 as "operation",  dim 3 as "product_display", dim 4 as "product_promotion".
Now use the loading of the 4 PCs as the two variables in place of the original 17 variables to form a new data set.
```{r}
store_data_sample_pca_1_1<-store_data_sample_pca_1[,-c(7,8,15,17)]
store_data_sample_pca_1_1[-12] <- scale(store_data_sample_pca_1_1[-12])

data.pc <- prcomp(store_data_sample_pca_1_1[,-12])
summary(data.pc)
plot(data.pc, type = "l")
fviz_pca_var(data.pc,
             col.var = "contrib", # Control variable color using their contributions to the PC
             gradient.cols = c("#70f6ff", "#00AFBB", "#ffd224",
                               "#d8ac00", "#FC4E07", "#a73203"),
             repel = TRUE,     # Avoid text overlapping
             ggtheme = theme_minimal()
             )
res.pca<-PCA(store_data_sample_pca_1_1[,-12],graph = FALSE)
var<-get_pca_var(res.pca)
corrplot(var$contrib,is.corr=FALSE)
```

```{r}
data.new_1 <- cbind(store_data_sample_pca_1_1[,12],data.pc$x[,1:4])
colnames(data.new_1)[1] <- c("cost")
colnames(data.new_1)[2] <- c("small_grocery_features")
colnames(data.new_1)[3] <- c("small_grocery_operation")
colnames(data.new_1)[4] <- c("small_grocery_product_display")
colnames(data.new_1)[5] <- c("small_grocery_product_promotion")
data.new_1<-as.data.frame(data.new_1)
```
PCA in regression
Use 4 new variables as independent variables and campaign cost as dependent variables to do the linear regression. It can be seen from the result that there is no significant correlation between each independent variable and the dependent variable. Therefore, the campaign cost of small grocery might be affected by displays.
```{r}
fit1 <- lm(cost ~small_grocery_features+small_grocery_operation+small_grocery_product_display+small_grocery_product_promotion, data.new_1)

summary(fit1)
```
## Gourmet supermarket
The scree plot shows that 4 PCs are the best for gourmet supermarket. For visualization purposes, we use the first four components. Because the dataset only contains one gourmet supermarket data, data about store area are all the same and dropped in the following analysis.

PC 1 explains about 36.8% of variability, PC 2 explains about 24.7% of variability, PC 3 explains about 13%, and PC 4 explains about 12%. The second and third graph both shows the correlation among variables. Arrows are closer to each other indicating a high correlation. 
*PC 1* is positively and highly correlated with the variables "store_sales.in.millions.","store_cost.in.millions.", "unit_sales.in.millions." and "SRP". *PC 2* is positively correlated with "gross_weight" and "net_weight". *PC 3* is positively and highly correlated with "unit_sales.in.millions" and "media". *PC 4* is positively and highly correlated with "units_per_case". Therefore, based on the correlation, Dim 1 is interpreted as "operation", dim 2 as "product_display",  dim 3 as "promotion", dim 4 as "product_design".
Now use the loading of the 4 PCs as the two variables in place of the original 36 variables to form a new data set.
```{r}
store_data_sample_pca_2_1<-store_data_sample_pca_2[,-c(7,8,10:13,15,17)]
store_data_sample_pca_2_1[,-8] <- scale(store_data_sample_pca_2_1[,-8])

data.pc2 <- prcomp(store_data_sample_pca_2_1[,-8])
summary(data.pc2)
plot(data.pc2, type = "l")
fviz_pca_var(data.pc2,
             col.var = "contrib", # Control variable color using their contributions to the PC
             gradient.cols = c("#70f6ff", "#00AFBB", "#ffd224",
                               "#d8ac00", "#FC4E07", "#a73203"),
             repel = TRUE,     # Avoid text overlapping
             ggtheme = theme_minimal()
             )
res.pca2<-PCA(store_data_sample_pca_2_1[,-8],graph = FALSE)
var2<-get_pca_var(res.pca2)
corrplot(var2$contrib,is.corr=FALSE)
```

```{r}
data.new2 <- cbind(store_data_sample_pca_2_1[,8],data.pc2$x[,1:5])
colnames(data.new2)[1] <- c("cost")
colnames(data.new2)[2] <- c("Gourmet_Supermarket_operation")
colnames(data.new2)[3] <- c("Gourmet_Supermarket_product_display")
colnames(data.new2)[5] <- c("Gourmet_Supermarket_promotion")
colnames(data.new2)[4] <- c("Gourmet_Supermarket_product_design")
data.new2<-as.data.frame(data.new2)
```
PCA in regression
Use 4 new variables as independent variables and campaign cost as dependent variables to do the linear regression. The result shows a significant correlation between promotion and product design and the dependent variables. Therefore, the campaign cost of a gourmet supermarket might be affected by promotion and product.
```{r}
fit2 <- lm(cost ~Gourmet_Supermarket_operation+Gourmet_Supermarket_product_display+Gourmet_Supermarket_promotion+Gourmet_Supermarket_product_design, data.new2)

summary(fit2)
```
## Supermarket
The scree plot shows that 4 PCs are the best for the supermarket. For visualisation purposes, we use the first four components.

PC 1 explains about 30.4% of variability, PC 2 explains about 22.3% of variability, PC 3 explains about 15.2%, and PC 4 explains about 9%. The second and third graph both shows the correlation among variables. Arrows are closer to each other indicating a high correlation. 
*PC 1* is positively and highly correlated with the variables store_sqft, grocery_sqft, frozen_sqft, meat_sqft and extra. *PC 2* is positively correlated with "store_sales.in.millions.","store_cost.in.millions.", "unit_sales.in.millions." and "SRP". *PC 3* is positively and highly correlated with "gross_weight" and "net_weight". *PC 4* is positively and highly correlated with "extra" and "media". Therefore, based on the correlation, Dim 1 is interpreted as "features", dim 2 as "operation",  dim 3 as "product_display", dim 4 as "product_promotion".

Now use the loading of the 4 PCs as the two variables in place of the original 36 variables to form a new data set.
```{r}
store_data_sample_pca_3_1<-store_data_sample_pca_3[,-c(7,8,15)]
store_data_sample_pca_3_1[-12] <- scale(store_data_sample_pca_3_1[-12])

data.pc3 <- prcomp(store_data_sample_pca_3_1[,-c(12)])
summary(data.pc3)
plot(data.pc3, type = "l")
fviz_pca_var(data.pc3,
             col.var = "contrib", # Control variable color using their contributions to the PC
             gradient.cols = c("#70f6ff", "#00AFBB", "#ffd224",
                               "#d8ac00", "#FC4E07", "#a73203"),
             repel = TRUE,     # Avoid text overlapping
             ggtheme = theme_minimal()
             )
res.pca3<-PCA(store_data_sample_pca_3_1[,-c(12)],graph = FALSE)
var3<-get_pca_var(res.pca3)

corrplot(var3$contrib,is.corr=FALSE)
```

```{r}
data.new3 <- cbind(store_data_sample_pca_3_1[,c(12)],data.pc3$x[,1:4])
colnames(data.new3)[1] <- c("cost")
colnames(data.new3)[2] <- c("supermarket_features")
colnames(data.new3)[3] <- c("supermarket_operation")
colnames(data.new3)[4] <- c("supermarket_product_display")
colnames(data.new3)[5] <- c("supermarket_promotion")
data.new3<-as.data.frame(data.new3)
```

PCA in regression
Use 4 new variables as independent variables and campaign cost as dependent variables to do the linear regression. The result shows a significant correlation between features and promotion and the dependent variables. Therefore, the campaign cost of the supermarket might be affected by features and promotions.
```{r}
fit3 <- lm(cost ~supermarket_features+supermarket_operation+supermarket_product_display+supermarket_promotion, data.new3)
summary(fit3)
```
## Deluxe_Supermarket

The scree plot shows that 4 PCs are the best for a deluxe supermarket.

PC 1 explains about 40.8% of the variability, PC 2 explains about 22.3%, PC 3 explains about 15.2%, and PC 4 explains about 7% of the variability. The second and third graph both shows the correlation among variables. Arrows are closer to each other indicating a high correlation. 
*PC 1* is positively and highly correlated with the variables store_sqft, grocery_sqft, frozen_sqft, meat_sqft and extra. *PC 2* is positively correlated with "store_sales.in.millions.","store_cost.in.millions.", "unit_sales.in.millions." and "SRP". *PC 3* is positively and highly correlated with "gross_weight" and "net_weight". *PC 4* is positively and highly correlated with "units_per_case". Therefore, based on the correlation, dim 1 is interpreted as "features", dim 2 as "operation",  dim 3 as "product_display", dim 4 as "product_sales".
Now use the loading of the 4 PCs as the two variables in place of the original 36 variables to form a new data set.
```{r}
store_data_sample_pca_4_1<-store_data_sample_pca_4[,-c(7,8,15)]
store_data_sample_pca_4_1[-12] <- scale(store_data_sample_pca_4_1[-12])

data.pc <- prcomp(store_data_sample_pca_4_1[,-c(12)])
summary(data.pc)
plot(data.pc, type = "l")
fviz_pca_var(data.pc,
             col.var = "contrib", # Control variable color using their contributions to the PC
             gradient.cols = c("#70f6ff", "#00AFBB", "#ffd224",
                               "#d8ac00", "#FC4E07", "#a73203"),
             repel = TRUE,     # Avoid text overlapping
             ggtheme = theme_minimal()
             )
res.pca<-PCA(store_data_sample_pca_4_1[,-c(12)],graph = FALSE)
var<-get_pca_var(res.pca)
corrplot(var$contrib,is.corr=FALSE)
```

```{r}
data.new_4 <- cbind(store_data_sample_pca_4_1[,c(12)],data.pc$x[,1:4])
data.new_4<-as.data.frame(data.new_4)
```
Specially, for PC 1(features), it can be seen that the curve fitting is parabola. Therefore, assign square to the value of PC1 in linear regression.
```{r}
data.new_4 %>% ggplot(aes(x=PC1, y=V1)) + geom_point() + geom_smooth()
```

```{r}
colnames(data.new_4)[1] <- c("cost")
colnames(data.new_4)[2] <- c("Deluxe_Supermarket_features")
colnames(data.new_4)[3] <- c("Deluxe_Supermarket_operation")
colnames(data.new_4)[4] <- c("Deluxe_Supermarket_display")
colnames(data.new_4)[5] <- c("Deluxe_Supermarket_product_Sales")
```
PCA in regression
Use 4 new variables as independent variables and campaign cost as dependent variables to do the linear regression. It can be seen from the result that there are significant correlations between features and features square and the dependent variables. Therefore, the campaign cost of deluxe supermarket might be affected by features and features square.
```{r}
fit4<-lm(cost~Deluxe_Supermarket_features+I(Deluxe_Supermarket_features^2)+Deluxe_Supermarket_operation+Deluxe_Supermarket_display+Deluxe_Supermarket_product_Sales,data=data.new_4)
summary(fit4)
```

## Conclusions
In Conclusion, different type of stores has different impacts on campaign cost.
1. For small groceries, the campaign cost is most impacted by display.
2. For gourmet supermarkets, promotion and product design dictate the campaign cost.
3. For supermarkets, the campaign cost is primarily affected by features and promotions.
4. For deluxe supermarkets, the campaign cost is primarily affected by features.