# library
```{r}
library(tidyverse)
library(factoextra)
library(cluster)
library(FactoMineR)
library(factoextra)
library(corrplot)
library(dplyr)
library(ggplot2)
library(clustMixType)
library(magrittr)
library(ISLR)
library(Rtsne)
library(RColorBrewer)
```

# Data Cleaning
```{r}
data<-read.csv("CFM_Campaigns.csv")
unique(data$sales_country)
data1<-data[data$sales_country=="USA",]
data1<-data1[,-3]
data1<-data1[,-2]
class(data1$houseowner)
data1$houseowner<-ifelse(data1$houseowner=="Y",TRUE,FALSE)
data1<-data1[,-6]
data1$gender<-ifelse(data1$gender=="F",0,1)
```

```{r}
unique(data1$store_type)
data1$store_type_1<-ifelse(data1$store_type=="Deluxe Supermarket",4,data1$store_type)
data1$store_type_1<-ifelse(data1$store_type_1=="Supermarket",3,data1$store_type_1)
data1$store_type_1<-ifelse(data1$store_type_1=="Gourmet Supermarket",2,data1$store_type_1)
data1$store_type_1<-ifelse(data1$store_type_1=="Small Grocery",1,data1$store_type_1)
```

```{r}
data1$marital_status<-ifelse(data1$marital_status=="M",TRUE,FALSE)
```

```{r}
unique(data1$media_type)
data1$radio<-str_detect(data1$media_type,"Radio")
data1$Daily_Paper<-str_detect(data1$media_type,"Daily Paper")
data1$In_Store_Coupon<-str_detect(data1$media_type,"In-Store Coupon")
data1$Product_Attachment<-str_detect(data1$media_type,"Product Attachment")
data1$Sunday_Paper<-str_detect(data1$media_type,"Sunday Paper")
data1$Street_Handout<-str_detect(data1$media_type,"Street Handout")
data1$Cash_Register_Handout<-str_detect(data1$media_type,"Cash Register Handout")
data1$Bulk_Mail<-str_detect(data1$media_type,"Bulk Mail" )
store_data<-data1
```

# PCA

This part aims to find out whether there is relationship between campaign cost and fundamental state of store or not. According to the dataset, it shows the fundamental state and operation cost of stores. Campaign cost might be affected by the fundamental state and operation cost stores. However, there are many correlated variables that the dataset contains. A data-reduction technique, PCA, is used to transforms them into a much smaller set of uncorrelated variables called *principal components*. Here is the fundamental state and promotion data of store includes:
1.*Numeric data*: "store_sales.in.millions.","store_cost.in.millions.", "unit_sales.in.millions.", "SRP"(Suggested retail price), "gross_weight", "net_weight", "store_sqft", "grocery_sqft","frozen_sqft", "meat_sqft";
2.*Categorical data*: "coffee_bar", "video_store", "salad_bar", "prepared_food", "florist",radio", "Daily_Paper", "In_Store_Coupon", "Product_Attachment", "Sunday_Paper", "Street_Handout", "Cash_Register_Handout", "Bulk_Mail";
For numeric data, PCA technique can be applied without any data cleaning. But for categorical data, the challenge is to find a suitable way to represent distances between variable categories and individuals in the factorial space. Therefore, all categorical datas are summarized to show the number of extra display and services of stores. All the fundamental state data of store are converted to numeric data now.
Also, because different types of store might have different effect of campaign cost,four store types, Deluxe Supermarket, Supermarket, Gourmet Supermarket, Small Grocery, are sorted to do the PCA analysis:
Deluxe Supermarket=4, Supermarket=3,Gourmet Supermarket=2, Small Grocery=1.


```{r}
store_data_sample<-store_data[sample(nrow(store_data),8000),]
```

```{r}
store_data_sample$media<-store_data_sample[,39]+store_data_sample[,40]+store_data_sample[,41]+store_data_sample[,42]+store_data_sample[,43]+store_data_sample[,44]+store_data_sample[,45]+store_data_sample[,46]
store_data_sample_pca<-store_data_sample[,-c(39:46)]
```

```{r}
store_data_sample_pca$extra<-store_data_sample_pca[31]+store_data_sample_pca[32]+store_data_sample_pca[33]+store_data_sample_pca[34]+store_data_sample_pca[35]
store_data_sample_pca<-store_data_sample_pca[,-c(1,5:17,24:26,31:36)]
```

```{r}
store_data_sample_pca_1<-store_data_sample_pca[store_data_sample_pca$store_type_1==1,]
store_data_sample_pca_2<-store_data_sample_pca[store_data_sample_pca$store_type_1==2,]
store_data_sample_pca_3<-store_data_sample_pca[store_data_sample_pca$store_type_1==3,]
store_data_sample_pca_4<-store_data_sample_pca[store_data_sample_pca$store_type_1==4,]
```

## Small grocery
For small grocery, the scree plot shows that 4 PCs are the best. For visualisation purpose, we use the first four components. 

PC 1 explains about 34% of variability, PC 2 explains about 24% of variability, PC 3 explains about 16% of variability and PC 4 explains about 8% of variability. Second and third graph both shows the correlation among variables. Arrows are closer to each other indicates the high correlation. 
*PC 1* is positively and highly correlated with the variables store_sqft, grocery_sqft, frozen_sqft, meat_sqft. *PC 2* is positively correlated with "store_sales.in.millions.","store_cost.in.millions.", "unit_sales.in.millions.". *PC 3* is positively and highly correlated with "gross_weight" and "net_weight". *PC 4* is positively and highly correlated with "units_per_case" and "media". Therefore, based on the correlation, Dim 1 is interpreted as "features", dim 2 as "operation",  dim 3 as "product_display", dim 4 as "product_promotion".
Now use the loading of the 4 PCs as the two variables in place of the original 17 variables to form a new data set.
```{r}
store_data_sample_pca_1_1<-store_data_sample_pca_1[,-c(7,8,15,17)]
store_data_sample_pca_1_1[-12] <- scale(store_data_sample_pca_1_1[-12])

data.pc <- prcomp(store_data_sample_pca_1_1[,-12])
summary(data.pc)
plot(data.pc, type = "l")
fviz_pca_var(data.pc,
             col.var = "contrib", # Control variable color using their contributions to the PC
             gradient.cols = c("#70f6ff", "#00AFBB", "#ffd224",
                               "#d8ac00", "#FC4E07", "#a73203"),
             repel = TRUE,     # Avoid text overlapping
             ggtheme = theme_minimal()
             )
res.pca<-PCA(store_data_sample_pca_1_1[,-12],graph = FALSE)
var<-get_pca_var(res.pca)
corrplot(var$contrib,is.corr=FALSE)
```

```{r}
data.new_1 <- cbind(store_data_sample_pca_1_1[,12],data.pc$x[,1:4])
colnames(data.new_1)[1] <- c("cost")
colnames(data.new_1)[2] <- c("small_grocery_features")
colnames(data.new_1)[3] <- c("small_grocery_operation")
colnames(data.new_1)[4] <- c("small_grocery_product_display")
colnames(data.new_1)[5] <- c("small_grocery_product_promotion")
data.new_1<-as.data.frame(data.new_1)
```
PCA in regression
Use 4 new variables as independent variables and campaign cost as dependent variable to do the linear regression. It can be seen from the result that there are no significant correlation between each independent variable and the dependent variable. Therefore, the campaign cost of small grocery might be affected by display.
```{r}
fit1 <- lm(cost ~small_grocery_features+small_grocery_operation+small_grocery_product_display+small_grocery_product_promotion, data.new_1)

summary(fit1)
```
## Gourmet supermarket
For gourmet supermarket, the scree plot shows that 4 PCs are the best. For visualization purpose, we use the first four components. Because dataset only contain one gourmet supermarket data, data about store area are all the same and dropped in following analysis.

PC 1 explains about 36.8% of variability, PC 2 explains about 24.7% of variability, PC 3 explains about 13% of variability and PC 4 explains about 12% of variability. Second and third graph both shows the correlation among variables. Arrows are closer to each other indicates the high correlation. 
*PC 1* is positively and highly correlated with the variables "store_sales.in.millions.","store_cost.in.millions.", "unit_sales.in.millions." and "SRP". *PC 2* is positively correlated with "gross_weight" and "net_weight". *PC 3* is positively and highly correlated with "unit_sales.in.millions" and "media". *PC 4* is positively and highly correlated with "units_per_case". Therefore, based on the correlation, Dim 1 is interpreted as "operation", dim 2 as "product_display",  dim 3 as "promotion", dim 4 as "product_design".
Now use the loading of the 4 PCs as the two variables in place of the original 36 variables to form a new data set.
```{r}
store_data_sample_pca_2_1<-store_data_sample_pca_2[,-c(7,8,10:13,15,17)]
store_data_sample_pca_2_1[,-8] <- scale(store_data_sample_pca_2_1[,-8])

data.pc2 <- prcomp(store_data_sample_pca_2_1[,-8])
summary(data.pc2)
plot(data.pc2, type = "l")
fviz_pca_var(data.pc2,
             col.var = "contrib", # Control variable color using their contributions to the PC
             gradient.cols = c("#70f6ff", "#00AFBB", "#ffd224",
                               "#d8ac00", "#FC4E07", "#a73203"),
             repel = TRUE,     # Avoid text overlapping
             ggtheme = theme_minimal()
             )
res.pca2<-PCA(store_data_sample_pca_2_1[,-8],graph = FALSE)
var2<-get_pca_var(res.pca2)
corrplot(var2$contrib,is.corr=FALSE)
```

```{r}
data.new2 <- cbind(store_data_sample_pca_2_1[,8],data.pc2$x[,1:5])
colnames(data.new2)[1] <- c("cost")
colnames(data.new2)[2] <- c("Gourmet_Supermarket_operation")
colnames(data.new2)[3] <- c("Gourmet_Supermarket_product_display")
colnames(data.new2)[5] <- c("Gourmet_Supermarket_promotion")
colnames(data.new2)[4] <- c("Gourmet_Supermarket_product_design")
data.new2<-as.data.frame(data.new2)
```
PCA in regression
Use 4 new variables as independent variables and campaign cost as dependent variable to do the linear regression. It can be seen from the result that there are significant correlation between promotion and product design and the dependent variables. Therefore, the campaign cost of gourmet supermarket might be affected by promotion and product.
```{r}
fit2 <- lm(cost ~Gourmet_Supermarket_operation+Gourmet_Supermarket_product_display+Gourmet_Supermarket_promotion+Gourmet_Supermarket_product_design, data.new2)

summary(fit2)
```
## Supermarket
For supermarket, the scree plot shows that 4 PCs are the best. For visualisation purpose, we use the first four components.

PC 1 explains about 30.4% of variability, PC 2 explains about 22.3% of variability, PC 3 explains about 15.2% of variability and PC 4 explains about 9% of variability. Second and third graph both shows the correlation among variables. Arrows are closer to each other indicates the high correlation. 
*PC 1* is positively and highly correlated with the variables store_sqft, grocery_sqft, frozen_sqft, meat_sqft and extra. *PC 2* is positively correlated with "store_sales.in.millions.","store_cost.in.millions.", "unit_sales.in.millions." and "SRP". *PC 3* is positively and highly correlated with "gross_weight" and "net_weight". *PC 4* is positively and highly correlated with "extra" and "media". Therefore, based on the correlation, Dim 1 is interpreted as "features", dim 2 as "operation",  dim 3 as "product_display", dim 4 as "product_promotion".

Now use the loading of the 4 PCs as the two variables in place of the original 36 variables to form a new data set.
```{r}
store_data_sample_pca_3_1<-store_data_sample_pca_3[,-c(7,8,15)]
store_data_sample_pca_3_1[-12] <- scale(store_data_sample_pca_3_1[-12])

data.pc3 <- prcomp(store_data_sample_pca_3_1[,-c(12)])
summary(data.pc3)
plot(data.pc3, type = "l")
fviz_pca_var(data.pc3,
             col.var = "contrib", # Control variable color using their contributions to the PC
             gradient.cols = c("#70f6ff", "#00AFBB", "#ffd224",
                               "#d8ac00", "#FC4E07", "#a73203"),
             repel = TRUE,     # Avoid text overlapping
             ggtheme = theme_minimal()
             )
res.pca3<-PCA(store_data_sample_pca_3_1[,-c(12)],graph = FALSE)
var3<-get_pca_var(res.pca3)

corrplot(var3$contrib,is.corr=FALSE)
```

```{r}
data.new3 <- cbind(store_data_sample_pca_3_1[,c(12)],data.pc3$x[,1:4])
colnames(data.new3)[1] <- c("cost")
colnames(data.new3)[2] <- c("supermarket_features")
colnames(data.new3)[3] <- c("supermarket_operation")
colnames(data.new3)[4] <- c("supermarket_product_display")
colnames(data.new3)[5] <- c("supermarket_promotion")
data.new3<-as.data.frame(data.new3)
```

PCA in regression
Use 4 new variables as independent variables and campaign cost as dependent variable to do the linear regression. It can be seen from the result that there are significant correlation between features and promotion and the dependent variables. Therefore, the campaign cost of supermarket might be affected by features and promotion.
```{r}
fit3 <- lm(cost ~supermarket_features+supermarket_operation+supermarket_product_display+supermarket_promotion, data.new3)
summary(fit3)
```
## Deluxe_Supermarket

For deluxe supermarket, the scree plot shows that 4 PCs are the best.

PC 1 explains about 40.8% of variability, PC 2 explains about 22.3% of variability, PC 3 explains about 15.2% of variability and PC 4 explains about 7% of variability. Second and third graph both shows the correlation among variables. Arrows are closer to each other indicates the high correlation. 
*PC 1* is positively and highly correlated with the variables store_sqft, grocery_sqft, frozen_sqft, meat_sqft and extra. *PC 2* is positively correlated with "store_sales.in.millions.","store_cost.in.millions.", "unit_sales.in.millions." and "SRP". *PC 3* is positively and highly correlated with "gross_weight" and "net_weight". *PC 4* is positively and highly correlated with "units_per_case". Therefore, based on the correlation, dim 1 is interpreted as "features", dim 2 as "operation",  dim 3 as "product_display", dim 4 as "product_sales".
Now use the loading of the 4 PCs as the two variables in place of the original 36 variables to form a new data set.
```{r}
store_data_sample_pca_4_1<-store_data_sample_pca_4[,-c(7,8,15)]
store_data_sample_pca_4_1[-12] <- scale(store_data_sample_pca_4_1[-12])

data.pc <- prcomp(store_data_sample_pca_4_1[,-c(12)])
summary(data.pc)
plot(data.pc, type = "l")
fviz_pca_var(data.pc,
             col.var = "contrib", # Control variable color using their contributions to the PC
             gradient.cols = c("#70f6ff", "#00AFBB", "#ffd224",
                               "#d8ac00", "#FC4E07", "#a73203"),
             repel = TRUE,     # Avoid text overlapping
             ggtheme = theme_minimal()
             )
res.pca<-PCA(store_data_sample_pca_4_1[,-c(12)],graph = FALSE)
var<-get_pca_var(res.pca)
corrplot(var$contrib,is.corr=FALSE)
```

```{r}
data.new_4 <- cbind(store_data_sample_pca_4_1[,c(12)],data.pc$x[,1:4])
data.new_4<-as.data.frame(data.new_4)
```
Specially, for PC 1(features), it can be seen that the curve fitting is parabola. Therefore, assign square to the value of PC1 in linear regression.
```{r}
data.new_4 %>% ggplot(aes(x=PC1, y=V1)) + geom_point() + geom_smooth()
```

```{r}
colnames(data.new_4)[1] <- c("cost")
colnames(data.new_4)[2] <- c("Deluxe_Supermarket_features")
colnames(data.new_4)[3] <- c("Deluxe_Supermarket_operation")
colnames(data.new_4)[4] <- c("Deluxe_Supermarket_display")
colnames(data.new_4)[5] <- c("Deluxe_Supermarket_product_Sales")
```
PCA in regression
Use 4 new variables as independent variables and campaign cost as dependent variable to do the linear regression. It can be seen from the result that there are significant correlation between features and features square and the dependent variables. Therefore, the campaign cost of deluxe supermarket might be affected by features and features square.
```{r}
fit4<-lm(cost~Deluxe_Supermarket_features+I(Deluxe_Supermarket_features^2)+Deluxe_Supermarket_operation+Deluxe_Supermarket_display+Deluxe_Supermarket_product_Sales,data=data.new_4)
summary(fit4)
```

## Conclusions of PCA & regression analysis
In Conclusion, different type of stores has different impact on campaign cost.
1.For small grocery, the campaign cost of small grocery might be affected by display.
2.For gourmet supermarket, the campaign cost of gourmet supermarket might be affected by promotion and product desugn.
3.For supermarket, the campaign cost of supermarket might be affected by features and promotion.
4.For deluxe supermarket, the campaign cost of deluxe supermarket might be affected by features.

# Cluster

A clustering method is utilized to identify the potential segments of consumers who responded to the campaign. The objective of using clustering is helping to better target consumers based on different stores and segmentation.

A Gower distance is applied to calculate the dissimilarities for mixed data types to better find out the differences among observations. Gower distance, according to the study, “can be used to measure how different two records are”(Loo,2022). The records include logical, categorical, numerical, and text, and a distance metric is calculated with a range from 0 to 1. Then the final distance matrix will be derived by computing user-specified weights, for example, an average. 

An 8000 sample was randomly selected due to limited capacity in R and the distance is calculated by using the package Daisy. 6 factors are put into considerations and they are: store_type, avg..yearly_income, education, occupation, number of children at home, avg_cars_at home. approx. 

## Calculate the Gower Distance 

```{r}
set.seed(123)
sample<-data1[sample(nrow(data1),8000),]
sample %<>% mutate_if(is.logical,as.numeric)
data_cluster <- sample %>% select(store_type,avg..yearly_income,education, occupation,num_children_at_home, avg_cars_at.home.approx.)
df1<-data.frame(lapply(data_cluster,factor))
```

```{r}
gower_dist <- daisy(df1,metric = "gower")
summary(gower_dist)
```

To check the sanity, a similar and dissimilar pair in the data is printed to assure that the calculation is sensible. From the two tables below, consumers 271 and 1 are rated to be the most similar given the six features used in the distance calculation, while consumers 1 and 2 are rated to be the most dissimilar. 

```{r}
gower_mat <- as.matrix(gower_dist)
df1[which(gower_mat == min(gower_mat[gower_mat != min(gower_mat)]),
        arr.ind = TRUE)[1, ], ]
```

```{r}
df1[which(gower_mat == max(gower_mat[gower_mat != max(gower_mat)]),
        arr.ind = TRUE)[1, ], ]
```

After the dissimilarity calculation, partitioning around medoids (PAM) was employed to identify the clusters. The cluster identification logic is similar to K-means, which starts from selecting k random entities as medoids. Then, it assigns every entity to its closest medoids based on the distance calculation. PAM will diagnose the observation that generates the lowest average distance and decide whether it should be re-assign as a new medoid. Lastly, if there is a need for a new medoid, it will circulate back to the second step to repeat the whole procedure again until there is no new medoid identified.

A silhouette width is created to help determine the number of clusters. Silhouette width presents the distance of observation to its cluster and in comparison with its closest neighboring cluster. Thus, the higher value means that there are greater differences among clusters. Based on the graph above, 3 clusters yield the highest value 

```{r}
sil_width <- c(NA)
for(i in 2:10){  
  pam_fit <- pam(gower_dist, 
                 diss = TRUE, 
                 k = i)  
  sil_width[i] <- pam_fit$silinfo$avg.width  
}
# Plot sihouette width (higher is better)
plot(1:10, sil_width,
     xlab = "Number of clusters",
     ylab = "Silhouette Width")
lines(1:10, sil_width)
```

A summary of the 3 clusters were developed to further look in their features. Based on the synopsis, cluster 1 contains 2236 samples (28%) and is mainly lower-middle income households with the majority of high-school degree background. Cluster 2 contains 3461 samples (43%) and is classified as middle and middle-higher-income households that 61% of them have bachelor's education background. Cluster 3 contains 2303 samples (29%) and is classified as lower income group with majority of the partial high school education background. 
```{r}
pam_fit <- pam(gower_dist, diss = TRUE, k = 3)
pam_results <- df1 %>%
  mutate(cluster = pam_fit$clustering) %>%
  group_by(cluster) %>%
  do(the_summary = summary(.))
pam_results$the_summary
```

```{r}
df1[pam_fit$medoids, ]
```

```{r}
tsne_obj <- Rtsne(gower_dist, is_distance = TRUE)
tsne_data <- tsne_obj$Y %>%
  data.frame() %>%
  setNames(c("X", "Y")) %>%
  mutate(cluster = factor(pam_fit$clustering))
ggplot(aes(x = X, y = Y), data = tsne_data) + geom_point(aes(color = cluster))
```

Combining cluster to the sample dataset  
```{r}
sample$cluster <- tsne_data$cluster
```
## Analysis of the cluster result

```{r}
store <- sample %>% group_by(cluster,store_type) %>% summarise(Count = n())%>% slice_max(Count, n=5)
```
## Number of consumers who shop at different stores from different segment
```{r}
nb.cols <- 40
mycolors <- colorRampPalette(brewer.pal(20, "Set2"))(nb.cols)
p4 <- ggplot(data=store, aes(x=cluster, y=Count, fill = store_type)) +
geom_bar(stat="identity", color="black", position=position_dodge())+ 
  labs(x="Cluster",y="Number of consumers from each cluster shop in each store")+
  ggtitle("Number of consumers shop in each store based Cluster")+
  scale_fill_manual(values = mycolors) +
  theme_minimal() + theme(legend.position = "top",legend.key.size = unit(0.5, 'cm'),legend.text = element_text(size=6),) + ylim(0,2100) + facet_wrap(~store_type) +expand_limits(x=c(0,4)) + scale_colour_discrete()
p4
```

The graph shows the preference of different types of stores in each segment when they consume goods. In summary, the majority all segments would love to shop in “Supermarket”, then it is “Deluxe Supermarket”.

Based on 3 segments of customers summarized from clustering, here are several related problems can be further explored with participation of 3 segments:
1. In each food mart, their preference of media types in marketing campaigns
2. In each food mart, their preference of food categories
3. Based on each food mart and each segment, the top 5 media types attract most sales 
4. Based on each food mart and each segment, the top 2 promotion names attract most sales 
 
## The top 10 media types that are used by consumer
```{r}
media_cluster <- sample %>% group_by(cluster,media_type) %>% summarise(Count = n()) %>% slice_max(Count, n=10)
```

```{r}
p1 <- ggplot(data=media_cluster, aes(x=cluster, y=Count, fill=media_type)) +
geom_bar(stat="identity", color="black", position=position_dodge())+ 
  labs(x="Cluster",y="Top 10 Media Type Counts")+
  ggtitle("Top 10 Media Type in each cluster")+
  scale_fill_manual(values = mycolors) +
  theme_minimal() + theme(legend.position = "top") + ylim(0,500)
p1
```

The graph above presents the top 5 media type that leads consumer to notice the campaign. According to the graph, Daily paper & radio are the two main ways to attract all three clusters of people from different stores. But for Deluxe Supermarket, product attachment and Sunday Paper also plays an important role to captivate consumers’ attention. For both supermarket and gourmet supermarket, consumers from all three clusters are more attracted through a combination usage of daily paper, radio, and TV. Interestingly, cash register handout are appealing to cluster 3 consumers who shop in supermarket. 


## Top 5 Media in each cluster
```{r}
store_cluster <- sample %>% group_by(store_type, cluster, media_type) %>% summarise(Count = n())%>% slice_max(Count, n=5)
```
```{r}
p2 <- ggplot(data=store_cluster, aes(x=cluster, y=Count, fill=media_type)) +
geom_bar(stat="identity", color="black", position=position_dodge())+ 
  labs(x="Cluster",y="Top 5 Media Type Counts")+
  ggtitle("Top 5 Media Type in each cluster")+
  scale_fill_manual(values = mycolors) +
  theme_minimal() + theme(legend.position = "top",legend.text = element_text(size=7)) + ylim(0,250) + facet_wrap(~store_type) +expand_limits(x=c(0,4))
p2
```
## Top 5 media types that attract most sales in each cluster
```{r}
sales_media_cluster <- sample %>% group_by(store_type,cluster,media_type) %>% summarise(sum = sum(store_sales.in.millions.)) %>% slice_max(sum, n=5)
```

```{r}
p5 <- ggplot(data=sales_media_cluster, aes(x=cluster, y=sum, fill = media_type)) +
geom_bar(stat="identity", color="black", position=position_dodge())+ 
  labs(x="Cluster",y="Top 5 media type that attract sales")+
  ggtitle("Top 5 Media Type that attract most sales")+
  scale_fill_manual(values = mycolors) +
  theme_minimal() + theme(legend.position = "top",legend.key.size = unit(0.5, 'cm'),legend.text = element_text(size=6),) + ylim(0,1600) + facet_wrap(~store_type) +expand_limits(x=c(0,4)) + scale_colour_discrete()
p5
```

The graph above shows what are the media type that generate more sales. Most of the top used media type from the previous graph are the main sales driver, while for deluxe supermarket, street handout becomes one of the sales driver even though its was not the major medium to communicate with consumers.

## Top 2 promotion name that attract most sales in each cluster
```{r}
promo_cluster <- sample %>% group_by(cluster,store_type,promotion_name) %>% summarise(sum = sum(store_sales.in.millions.))%>% slice_max(sum, n=2)
```

```{r}
p3 <- ggplot(data=promo_cluster, aes(x=cluster, y=sum, fill = promotion_name)) +
geom_bar(stat="identity", color="black", position=position_dodge())+ 
  labs(x="Cluster",y="Top 2 Promotion Name that attract sales")+
  ggtitle("Top 2 promotion name that attract most sales")+
  scale_fill_manual(values = mycolors) +
  theme_minimal() + theme(legend.position = "top",legend.key.size = unit(0.5, 'cm'),legend.text = element_text(size=6),) + ylim(0,1100) + facet_wrap(~store_type) +expand_limits(x=c(0,4)) + scale_colour_discrete()
p3
```

In terms of the usage of promotion name, “Bag Stuffers” and “ Cash Register Lottery” can attract most sales in for all three clusters in the Deluxe Supermarket. While promotion names such as “undefeatable price saver”, “High Roller Savings” names that are strongly related sales and money saving will attract all three clusters of consumer to shop in Gourmet and Supermarket. Moreover, from the “weekend markdown” we can also infer that most of the supermarket consumers are shopping during the weekend, therefore, more sales and promotional activities can be conducted to drive more sales and traffic. 
```{r}
data_cate <- sample %>% group_by(store_type,cluster,food_category)  %>% summarise(count_cate=n()) %>% slice_max(count_cate,n=5)
ggplot(data=data_cate, aes(x=cluster, y=count_cate, fill=food_category))+geom_bar(stat="identity", color="black", position=position_dodge())+labs(x="store type",y="Top 5 Food categories")+scale_fill_manual(values = mycolors)+facet_wrap(~store_type) +theme_minimal() +ggtitle("Top 5 food Categories purchased by each cluster")
```

The graph above presents the top 5 food categories that consumers usually consume in each food mart. According to the graph, “snack foods”, “vegetables” and “dairy” are the top 3 categories bought by consumers in all segments. In cluster 1, consumers bought more “fruit” in supermarket and bought more bread in small grocery and gourmet supermarket. In cluster 2, consumers bought fruits in all kinds of food marts. In cluster 3, consumers only bought more canned food in deluxe supermarket and gourmet supermarket.

## Conclusion & Recommendation

Based on the analysis of the cluster above, recommendations are given to help convenient food mart to better implement its campaign. 

Different types of store can utilize different types of campaign to attract different clusters of consumers. Food Mart not only should continue its campaign through daily paper, radio and TV but add more featuring campaign. For Deluxe Supermarket, they can shift more attention on product attachment to deliver the campaign message. Even though most of shoppers in Deluxe Supermarket notice campaign through in-store coupon, when it comes to attribution to sales, in-store coupon are less effectively compare to other types of media. Therefore, Deluxe Supermarket can use more product attachment, radio, and daily paper to increase its presence among the consumers. The major five media types that supermarket are currently using are daily paper, radio, bulk mail, and TV. However, consumers from cluster 1 and 3 are attracted through in-store coupon; therefore, using more in-store coupon can appeal and reach out to more consumers from cluster 1 and 3. 

The promotion name reflects consumers’ behavior as well as their preferred type of promotion. Since most of the supermarket consumers were attracted by “Weekend Markdown”, supermarket can provide more in-store promotional activities and have more staffs in stores ensure the service quality during the weekend. Since cluster 1 and 3 are mostly attracted by “Shelf clearing”, “Emptiness”, the in-store activity can add more promotion similar to shelf clearing to generate more traffics and sales. 

In terms of the food categories each stores choose to do promotion, all four types of stores can add more promotions on vegetables, snacks and diary, since most of the consumers are purchasing these three categories. Besides, there are a few categories that consumers bought more units in a certain kind of food marts. For example, cluster 1 bought more fruit in supermarket and bought more bread in small grocery and gourmet supermarket. In cluster 3, consumers bought more bread in deluxe supermarket. Therefore, each type of food marts could select the most popular food categories to do promotion and when choosing the media type and purchasing name, they could consider the preference of consumers who bought more units of this category in their type of stores. For instance, the supermarket could do more promotion on fruits using promotion name like “Shelf clearing”, and “Emptiness” to especially attract cluster 1 consumers.

Another insight can be drawn from the clustering is that these three clusters share similar preferences in store types, food categories, media types, and promotional names, which reveals that even though a cluster can be developed based on different demographics and store types, consumers still share similar preferences in their purchases. It’s difficult to cluster a certain type of consumers who mainly go to one certain type of food mart, consume several certain types of food e.g.since there will be other influencing factors such as location of the food mart and store capacity.